Multisensor Architecture for an Intersection Management System

### 2019-01-22 ch1-introduction.tex
Added information about contribution in section 4.1 (Articles, events and journals)

Chapter 4 summarizes the conclusions of the development of the whole work, remarking on contributions made like software and applications generated, academic products, and future developments and improvements for the system, including application performance, platforms upgrade, UX/UI improvements, scalability and integration with IOT and Smart Cities solutions.

>>>>

Chapter 4 summarizes the conclusions of the development of the whole work, remarking on contributions made like software and applications generated, academic products, and future developments and improvements for the system, including application performance, platforms upgrade, UX/UI improvements, scalability and integration with Internet of Things (IOT) and Smart Cities solutions.

### 2019-01-22 ch5-conclusions.tex
Added TODOs
Added information about contribution in section 4.1 (Articles, events and journals)

On the other side, a couple of articles are being reviewed previous to be submmited to a journal. One article is a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation, based on chapters 2 and 3.

>>>>

%\todo{Detail contributions}

On the other side, a couple of articles have been derived from this work. One article, titled "\textit{A Review on Intersection Management Systems and Recent IoT Integrated Approaches}" is a review on intersection management systems, based on chapter 1. This article is also focused on how Internet of Things (IOT) has been used for IMS and it remarks recent developments and deployments on this field. This article has been submitted to the IEEE 5th World Forum on Internet of Things, which will be held during April 2019 at Limerick, Ireland \footnote{http://wfiot2019.iot.ieee.org/}.

 Another article based on chapters 2 and 3, presents a full description of the architecture and an example implementation. This article is still on writing stage and is intended to be submitted to the national journal DYNA\footnote{https://revistas.unal.edu.co/index.php/dyna}.
